Liptschiz

### 2024-02-22 Reports/tech_report1.tex
fix mistakes

>>>>

\section{February 21 experiments}

\subsection{Find best open ReLU for layer 3 for normal 5x100, new pure y-constraints}

This experiment is to find the best open ReLU number for layer 3 normal 5x100 with new pure-y constraints constraints.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the partial output file name is \verb*|DL_V0p3_find_open_number_layer3_0.txt,DL_V0p3_find_open_number_layer3_1.txt,DL_V0p3_find_open_number_layer3_2.txt,DL_V0p3_find_open_number_layer3_3.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 022100102024

	\item\emph{Open $\ReLU$ number:} Open 20,23,26,29,32 ReLU nodes for each node.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network. 
\end{itemize}

We will use the following new constraints, and keep the old variables and constraints (will not use them at present).

The new constraints are: \begin{align*}
	\hat{y}_i \leq a \gamma_i \hspace*{2ex} &\wedge \hspace*{2ex}\hat{y} \geq y_i - a \gamma_i\\
	\hat{y}_i \geq (a-1) \gamma_i  \hspace*{2ex} &\wedge \hspace*{2ex} \hat{y} \leq y_i + (1-a) \gamma_i,
\end{align*} Here, $y_i$ is the variable that represents $x_i-x'_i$, $\hat{y}_i$ represents $\hat{x}_i-\hat{x}'_i$, $a$ is a binary variable, $\gamma_i$ is the upper bound of $x_i-x'_i$.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_find_open_number_layer3_0.txt,DL_V0p3_find_open_number_layer3_1.txt,DL_V0p3_find_open_number_layer3_2.txt,DL_V0p3_find_open_number_layer3_3.txt|.

	\item \emph{Total time:}

	\item \emph{Key results:} Due to some mistakes we only have open to 29 nodes. $\gamma$ for different open numbers are

	0.2280277192602802          0.2303032016837368         open 20

	0.2168232231501058          0.21899023640990567      open 23

	0.20544377026809135        0.2103601628177343        open 26

     0.19510091588084752   0.20836893269039397   open 29

	 This is much better than previous methods.

\subsection{Compute the gamma of layer 3 for normal 5x100, new pure y-constraints}

This experiment is to  compute the gamma of layer 3 normal 5x100 with new pure-y constraints constraints.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the output file name is \verb*|DL_V0p3_layer3_open_27.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 3 with open 27 ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 022100102024

	\item\emph{Open $\ReLU$ number:} Open 27 ReLU nodes for each node.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network. 
\end{itemize}

We will use the following new constraints, and keep the old variables and constraints (will not use them at present).

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer3_open_27.txt|.

	\item \emph{Total time:} 30740s.

	\item \emph{Key results:} The average gamma of this layer is:  0.20506045995399397

	The average solution for gamma of this layer is:  0.1998876293451762

	\item  \emph{Binary file:} \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|. This file stores the gammas in this test.

### 2024-02-22 lipschitz/valabstraction.tex
fix mistakes

\begin{align*}
	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
\end{align*}

>>>>

\begin{align*}
	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(a-1)\alpha_i \\
\end{align*}
